Subsegmental language detection in Celtic language text

### 2014-06-27 codeswitch-cltw-2014/codeswitch_camera_ready.tex
evaluation review 2.7
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@55021 72bbbca6-d526-0410-a7d9-f06f51895060
review 2.2
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@55022 72bbbca6-d526-0410-a7d9-f06f51895060

%Try1: akshay minocha
%
% File coling2014.tex
%
% Contact: jwagner@computing.dcu.ie

@@

Code-switching and segment detection problems have been the subject of previous research. A good deal of work
has been done on detecting code-switched segments in speech data \cite{chan2004detection,lyu2006language}.
It is seen that language modelling techniques have shown promise earlier, such as in \newcite{yu2013identification} 
the experiment on Mandarin-Taiwanese code-switched sentences show a high accuracy in terms of detecting code-switched sentences. \\

\newcite{chan2004detection} has made use of the bi-phone probabilities and calculated them to measure a confidence metric, 
to \cite{lyu2006language} which has made use of a classification method, named syllable-based duration classification, 
which uses the tonal syllable properties along with the speech signals to help predict the code switch points. \newcite{yeong2010language} 
uses syllable structure information to identify words in code-switched text in Malay-English, however they did not 
recognise segments in running text, only identifying individual words.

@@

We hand-annotated a small evaluation set from a selection of posts to a popular microblogging site\footnote{\url{http://indigenoustweets.blogspot.in/2013/12/mapping-celtic-twittersphere.html}}. The posts `tweets' were filtered into three sets which had been identified as Irish, Welsh and Breton.  Certain tokens were escaped from the data, such as mentioned (which are preceded by an \texttt{@} symbol), subject tags `hashtags' which are preceded by a \texttt{\#} symbol), hyperlinks and the sequence \texttt{rt} which stands for `re-tweet'. An example of the content of our corpus after hand annotation is given in Figure~\ref{fig:tweets}. All of the tweets had at least one instance of code-switching.

>>>>

%Try2: akshay minocha
%
% File coling2014.tex
%
% Contact: jwagner@computing.dcu.ie

@@

Code-switching and segment detection problems have been the subject of previous research. A good deal of work
has been done on detecting code-switched segments in speech data \cite{chan2004detection,lyu2006language}.
It is seen that language modelling techniques have shown promise earlier, such as in \newcite{yu2013identification}, 
the experiment on Mandarin-Taiwanese code-switched sentences show a high accuracy in terms of detecting code-switched sentences. \\

In \newcite{chan2004detection} the authors have made use of the bi-phone probabilities and calculated them to measure a confidence metric, 
to \cite{lyu2006language} which has made use of a classification method, named syllable-based duration classification, 
which uses the tonal syllable properties along with the speech signals to help predict the code switch points. In \newcite{yeong2010language} 
 the authors use syllable structure information to identify words in code-switched text in Malay-English, however they did not 
recognise segments in running text, only identifying individual words.

@@

We hand-annotated a small evaluation set from a selection of posts to a popular microblogging site\footnote{\url{http://indigenoustweets.blogspot.in/2013/12/mapping-celtic-twittersphere.html}}. The posts `tweets' were filtered into three sets which had been identified as Irish, Welsh and Breton using the langid tool.  Certain tokens were escaped from the data, such as mentioned (which are preceded by an \texttt{@} symbol), subject tags `hashtags' which are preceded by a \texttt{\#} symbol), hyperlinks and the sequence \texttt{rt} which stands for `re-tweet'. An example of the content of our corpus after hand annotation is given in Figure~\ref{fig:tweets}. All of the tweets had at least one instance of code-switching.
